Differential Expression - HBCC - sgACC - Dx

### 2020-05-20 individual-cohorts/HBCC_sgACC_DE.Rmd
fix dream input? did not fail in other cohorts

# Model categorical variables as random to report variance fractions
formula_for_variance_fractions = sapply(1:length(col_type$class), function(i){
  switch(col_type$class[i], 
    "factor" = paste0('(1|', col_type$variable[i], ')'),
    "numeric" = paste0('scale(', col_type$variable[i], ')')
  )
  })

@@

violin_plot <- variancePartition::fitExtractVarPartModel(VOOM.GENE_EXPRESSION,
                                                         formula = formula_for_variance_fractions,
                                                         data = COVARIATES)

>>>>

# Model categorical variables as random to report variance fractions
formula_for_variance_fractions = sapply(1:length(col_type$class), function(i){
  switch(col_type$class[i], 
    "factor" = paste0('(1|', col_type$variable[i], ')'),
    "numeric" = paste0(col_type$variable[i])
  )
  })

@@

violin_plot <- variancePartition::fitExtractVarPartModel(VOOM.GENE_EXPRESSION$E,
                                                         formula = formula_for_variance_fractions,
                                                         data = COVARIATES)
